Probabilities of polar aligned disks in binary star systems

### 2024-04-16 src/tex/ms.tex
Use bold font for vecotors

\begin{equation}
\begin{aligned}
    \hat{z} & = \vec{L}/\|\vec{L}\| \\
    \hat{x} & = \vec{e}/\|\vec{e}\| \\
    \hat{y} & = - \hat{x} \times \hat{z}
    \label{eq:coords}
\end{aligned}
\end{equation}
\RGM{The journal requires that you write vectors as $\bm{L}$, for example.}
We can then compute $i$ and $\Omega$ from the specific angular momentum $\vec{h}$.

\begin{equation}
    \cos{i} = \frac{\vec{h} \cdot \hat{z}}{\|\vec{h}\|}
    \label{eq:inclination}
\end{equation}

\begin{equation}
    \Omega = \arctantwo (\vec{h} \cdot \hat{x}, -\vec{h} \cdot \hat{y})
    \label{eq:omega}
\end{equation}
\RGM{no need to introduce $\bm{h}$ I think, you can  use $\bm{L}$ or $\bm{l}=\bm{L}/|\bm{L}|$}

>>>>

\begin{equation}
\begin{aligned}
    \hat{\bm{z}} & = \bm{L}/\|\bm{L}\| \\
    \hat{\bm{x}} & = \bm{e}/\|\bm{e}\| \\
    \hat{\bm{y}} & = - \hat{\bm{x}} \times \hat{\bm{z}}
    \label{eq:coords}
\end{aligned}
\end{equation}
We can then compute $i$ and $\Omega$ from the angular momentum $\bm{L}$.

\begin{equation}
    \cos{i} = \frac{\bm{L} \cdot \hat{z}}{\|\bm{L}\|}
    \label{eq:inclination}
\end{equation}

\begin{equation}
    \Omega = \arctantwo (\bm{L} \cdot \hat{\bm{x}}, -\bm{L} \cdot \hat{\bm{y}})
    \label{eq:omega}
\end{equation}
